Zonotoop--a large scale aggregating data warehouse for time-series-based data. [DRAFT]

### 2009-05-04 doc/report/msc-report.tex
minor additions and changes to report.

\author{Per Andersson, Fredrik M{\"o}llerstrand}
\title{OHM -- OHM HBase Masseuse [DRAFT]}

@@

\chapter{OHM}

We have built a system--henceforth called OHM--which has the goal of being
a large scale data warehouse for time-series based log-like data sources.

@@

\subsection{Query language}

@@

The user writes MapReduce programs which imports log-like data to the data
store.

After the data is imported a metadata scanner is run which creates metadata
about the imported data.

\section{Store data}

@@

When data is exchanged between OHM and the user either
JSON\footnote{JavaScript Object Notation} is transported over a RESTful
interface or data is transported with Thrift.

@@

>>>>

\author{Per Andersson, Fredrik M{\"o}llerstrand}
\title{Zonotoop--a large scale aggregating data warehouse for
time-series-based data. [DRAFT]}

@@

\chapter{Usage}

We have built a system--henceforth called OHM--which has the goal of being
a large scale aggregating data warehouse for time-series-based log-like
data sources.

@@

@@

The user writes the map part of the MapReduce programs which imports
log-like data to the data store. The reduce step is taken care of by OHM,
which uses sum reducer that simply sums up values with the same keys.

\subsection{User mappers}

Import jobs use mappers defined by the user, either in Python or Java.
Mappers written by the user import each line from the input file and set
the arguments to the map function, key and value, as line number and line
contents, respectively. The user can then perform computations on these
entities and finally yield the results as a dictionary. The resulting
dictionary will be interpreted by OHM and stored accordingly.

\section{Storing data}

@@

Importing data to OHM is as simple as the user defines a mapper--the first
half of a MapReduce program--which is run over a file that resides on
HDFS\footnote{Hadoop Distributed Filesystem}.

Data is stored on Apache HBase

Exporting data

and the user 
JSON\footnote{JavaScript Object Notation} is transported over a RESTful
interface or data is transported with Thrift.

@@

The user's datasets are defined using YAML--a human friendly data
serialization standard.
